Report

### 2021-06-10 Rmd/report.Rmd
Add 21 mo monolinguals analysis

# load data
gaze <- readRDS(here("Data", "Gaze", "processed.rds"))
attrition <- readRDS(here("Results", "attrition.rds"))
participants <- readRDS(here("Data", "Participants", "participants.rds")) %>% 
	left_join(distinct(attrition, participant, age_group, valid_participant)) %>% 
	drop_na(participant)
fit <- readRDS(here("Results", "fit.rds"))

@@

# Results

@@

```{r fixed_effects_table, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
main_effects <- confint.merMod(fit, method = "Wald") %>% 
	as.data.frame() %>% 
	clean_names() %>% 
	drop_na(x2_5_percent) %>%
	rownames_to_column("term") %>% 
	right_join(clean_names(tidy(fit, effects = "fixed"))) %>% 
	select(term, estimate, std_error, conf_lower = x2_5_percent, conf_upper = x97_5_percent,
		   statistic, df, p_value) %>% 
	gt() %>% 
	fmt_number(2:7) %>% 
	fmt_number(8, decimals = 3) %>% 
	cols_merge(starts_with("conf_"), pattern = "[{1}, {2}]") %>% 
	cols_label(
		term = md("**Predictor**"),
		estimate = md("**Estimate**"),
		std_error = md("**SE**"),
		conf_lower = md("**CI<sub>95%</sub>**"),
		statistic = md("***t***"),
		df = md("**df**"),
		p_value = md("***p***")
	) %>% 
	tab_style(
		style = list(
			cell_fill(color = "#F9E3D6")
		),
		locations = cells_body(
			columns = everything(),
			rows = p_value < 0.05
		)
	)
gtsave(data = main_effects, filename = "main_effects.png", path = here("Figures"))
main_effects
```

@@

@@

## Appendix 1: Individual attrition rates

```{r attrition_individual, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=12}

attrition %>%
	left_join(select(participants, location, lp, participant, date_test)) %>% 
	drop_na(trial_type) %>% 
	group_by(participant, lp, location, date_test, age_group, trial_type, valid_participant, valid_other) %>% 
	summarise(valid_trial_count = sum(valid_trial, na.rm = TRUE),
			  .groups = "drop") %>% 
	pivot_wider(names_from = trial_type, values_from = valid_trial_count) %>% 
	clean_names() %>% 
	mutate(
		participant = str_remove(participant, "cognatepriming"),
		cognate = paste0(cognate, " (", round(cognate/8, 2), "%)"),
		non_cognate = paste0(non_cognate, " (", round(non_cognate/8, 2), "%)"),
		unrelated = paste0(unrelated, " (", round(unrelated/8, 2), "%)"),
	) %>% 
	arrange(location, date_test) %>% 
	relocate(
		participant, location, date_test,
		age_group, lp, cognate, non_cognate,
		unrelated, valid_other, valid_participant) %>% 
	gt() %>% 
	tab_spanner(
		"Valid trials (%) by trial type",
		c("cognate", "non_cognate", "unrelated")
	) %>% 
	cols_label(
		participant = "Participant",
		location = "Location",
		date_test = "Date",
		lp = "Group",
		age_group = "Age",
		valid_participant = "Valid trials",
		valid_other = "Valid (other)?",
		cognate = "Cognate",
		non_cognate = "Non-cognate",
		unrelated = "Unrelated"
	) %>% 
	tab_style(
		style = list(
			cell_fill(color = "#00FA9A")
		),
		locations = cells_body(
			columns = c("valid_participant"),
			rows = valid_participant
		)
	) %>% 
	tab_style(
		style = list(
			cell_fill(color = "#00FA9A")
		),
		locations = cells_body(
			columns = c("valid_other"),
			rows = valid_other
		)
	)

>>>>

# load data
gaze <- readRDS(here("Data", "Gaze", "processed.rds"))
attrition <- readRDS(here("Results", "attrition.rds"))
participants <- readRDS(here("Data", "Participants", "participants.rds")) %>% 
	left_join(distinct(attrition, participant, age_group, valid_participant)) %>% 
	drop_na(participant)
fit <- readRDS(here("Results", "fit.rds"))
fit_21_mon <- readRDS(here("Results", "fit_21_mon.rds"))

@@

# Results {.tabset .tab-pills}

@@

```{r fixed_effects_table, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
main_effects <- confint.merMod(fit, method = "Wald") %>% 
	as.data.frame() %>% 
	clean_names() %>% 
	drop_na(x2_5_percent) %>%
	rownames_to_column("term") %>% 
	right_join(clean_names(tidy(fit, effects = "fixed"))) %>% 
	select(term, estimate, std_error, conf_lower = x2_5_percent, conf_upper = x97_5_percent,
		   statistic, df, p_value) %>% 
	gt() %>% 
	fmt_number(2:7) %>% 
	fmt_number(8, decimals = 3) %>% 
	cols_merge(starts_with("conf_"), pattern = "[{1}, {2}]") %>% 
	cols_label(
		term = md("**Predictor**"),
		estimate = md("**Estimate**"),
		std_error = md("**SE**"),
		conf_lower = md("**CI<sub>95%</sub>**"),
		statistic = md("***t***"),
		df = md("**df**"),
		p_value = md("***p***")
	) %>% 
	tab_style(
		style = list(
			cell_fill(color = "#F9E3D6")
		),
		locations = cells_body(
			columns = everything(),
			rows = p_value < 0.05
		)
	)

gtsave(data = main_effects, filename = "main_effects.png", path = here("Figures"))
main_effects
```

@@

#### 21 month-old monolinguals

```{r fixef_21_mon, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
main_effects <- confint.merMod(fit_21_mon, method = "Wald") %>% 
	as.data.frame() %>% 
	clean_names() %>% 
	drop_na(x2_5_percent) %>%
	rownames_to_column("term") %>% 
	right_join(clean_names(tidy(fit_21_mon, effects = "fixed"))) %>% 
	select(term, estimate, std_error, conf_lower = x2_5_percent, conf_upper = x97_5_percent,
		   statistic, df, p_value) %>% 
	gt() %>% 
	fmt_number(2:7) %>% 
	fmt_number(8, decimals = 3) %>% 
	cols_merge(starts_with("conf_"), pattern = "[{1}, {2}]") %>% 
	cols_label(
		term = md("**Predictor**"),
		estimate = md("**Estimate**"),
		std_error = md("**SE**"),
		conf_lower = md("**CI<sub>95%</sub>**"),
		statistic = md("***t***"),
		df = md("**df**"),
		p_value = md("***p***")
	) %>% 
	tab_style(
		style = list(
			cell_fill(color = "#F9E3D6")
		),
		locations = cells_body(
			columns = everything(),
			rows = p_value < 0.05
		)
	)

gtsave(data = main_effects, filename = "main_effects_21_mon.png", path = here("Figures"))
main_effects

```{r gaze_time_21_mon, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
sample_size <- participants %>% 
	filter(valid_participant, age_group=="21 months", lp=="Monolingual") %>% 
	count(age_group, lp)

augment(fit_21_mon) %>% 
	mutate(.fitted_prob = logit_to_prob(.fitted)) %>% 
	ggplot() +
	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
	stat_summary(aes(x = ot1, y = .fitted_prob, colour = trial_type, fill = trial_type),
				 fun.data = mean_se, geom = "ribbon", alpha = 0.5, colour = NA) +
	stat_summary(aes(x = ot1, y = .fitted_prob, colour = trial_type, fill = trial_type),
				 fun = mean, geom = "line", size = 1) +
	# stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
	geom_text(data = sample_size,
			  aes(x = -0.3, y = 0.95, label = paste0("N = ", n)),
			  show.legend = FALSE,
			  colour = "black", fill = "black") +
	labs(x = "Time bin (100 ms)", y = "Pr(Target fixation)",
		 colour = "Trial type", fill = "Trial type") +
	scale_y_continuous(limits = c(0, 1), labels = scales::percent) + 
	scale_x_continuous(breaks = unique(gaze$ot1), labels = unique(gaze$time_bin)) +
	theme(
		axis.title.y = element_blank(),
		axis.text = element_text(size = 7),
		legend.position = "left"
	) +

	augment(fit_21_mon) %>% 
	mutate(elog_prob = logit_to_prob(elog)) %>% 
	group_by(participant, trial_type) %>% 
	summarise(elog_prob = mean(elog_prob, na.rm = TRUE)) %>% 
	ggplot(aes(trial_type, elog_prob, fill = trial_type, colour = trial_type)) +
	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
	geom_violin(show.legend = FALSE) +
	geom_boxplot(width = 0.1, outlier.colour = NA, fill = "white", colour = "black") +
	labs(x = "Trial type", y = "Pr(Target fixation)",
		 colour = "Trial type", fill = "Trial type") +
	scale_y_continuous(limits = c(0, 1), labels = scales::percent) + 
	theme(
		axis.title = element_blank(),
		axis.ticks = element_blank(),
		axis.text.x = element_blank(),
		axis.text.y = element_blank()
	) +
	plot_layout(ncol = 2, guides = "collect", widths = c(0.75, 0.25)) &
	plot_annotation(
		caption = "A: Marginal means of the multilevel model, plotted in separate panels for monolinguals and bilinguals, across age\ngroups. Sample sizes are indicated at the upper left corner in each panel. The first and last 300 ms in each trial\nwere trimmed before the analysis. B: mean observed probability of target looking, aggregated by participant.",
		tag_levels = "A") &
	theme_custom() &
	theme(
		legend.position = "right",
		plot.caption = element_text(size = 10, hjust = 0),
		plot.caption.position = "plot"
	) &
	ggsave(here("Figures", "emmeans_21_mon.png"))
```

@@
